The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-21 paper.tex
update

\begin{abstract}
% out of the Galactic center on either side of the Galactic disk
\end{abstract}

@@

  For these two reasons,\
  we have ignored the CR diffusion and the magnetic field throughout\
  the simulation.\
  Also, we do not simulate the spectral evolution of the CR\
  and assume the pressure ratio of CR to gas is much less than 1 so that\
  the contribution of CR pressure gradient to the momentum of the gas can be ignored.\
  (we will see that the pressure ratio is around 0.1--0.2 throughtout the bubbles formation)\
  In addition, we neglect the cooling and heating processes of CRs,\
  such as energy losses due to synchrotron and inverse Compton emission,\
  and CR reacceleration in shocks/turbulences.

@@

In this work, we introduce a thin, dense disk composed of interstellar medium\
to divert the inclined jet at an angle $45^{\circ}$\
to the disk normal in the past energetic event of the central SMBH.

@@

\item The Galactic bubbles are nearly symmetric about the Galactic plane albeit the jet is at an angle $45^{\circ}$\
      with respect to the disc normal.\
      The broad agreement between simulated and observed multiwavelength features\
      provides supporting evidence for the inclined jet scenario, and also\
      releases the caveat given by earlier simulation-based studies:\
      the jets shall be vertical to the disc normal.
\item The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
      The ambient stratification facilitates the eROSITA bubbles elongation significantly.
      The development of the reverse shocks (the innermost bubbles) are always associated with the dense disc.
\item The edge of the eROSITA bubbles is a forward shock,\
      originally driven by an oblique bipolar jets emanating from the GC 12.39 million years ago,\
      and significantly stretched by the stratified atmosphere afterwards.
\item Followed by the forward shock is a tangling contact discontinuity,\
      which we interpret as the edge of the \textit{Fermi} bubbles.\
      The nature of the \textit{Fermi} bubbles is essentially a turbulent and high-temperature ($\sim2$ keV)\
      plasma in pressure balance with the external medium. Associated with the Galactic magnetic field\
      will lead to the stochastic acceleration of CRe, and probably balanced with the IC and synchrotron cooling.\
      We will investigate the competition between CRe acceleration and radiative cooling in a future work.
\item According to the microwave and leptonic gamma-ray spectra, the best-fitting\
      CRe power-law index is found to be -2.4.
\item The same leptotonic CRe can simultaneously\
      account for the \textit{Fermi} bubbles and haze emission suggested that\
      they are physically related around the GC,\
      and that the magnetic fields within the bubbles are close to the exponentially distributed\
      Galactic magnetic field.
\end{itemize}

%Over the past few years, there have been numerous efforts,\
%both observational and theoretical, to uncover the nature of the Galactic bubbles.
%
%
%Spektr-RG \citep{Sunyaev2021} and eROSITA \citep{Predehl2021}

We have found qualitative similarities between the results our simulations\
and the observed spectrum and morphological structure of the Galactic bubbles.

Since the jets encounter a larger column depth of clouds along their path,\
they interact more strongly with the dense ISM.\
The jets do not immediately clear a channel along the inclined axis of launch.\
Rather, the dense clouds deflect the jets, which then decelerate\
and launch a sub-relativistic outflow along the minor axis following the path of least resistance.

Assuming that a relativistic electron population of spectral
index x = 2.2 gives rise to the microwave haze via synchrotron
emission.

%We therefore suggest that the Fermi bubbles and the eROSITA structure are physically related,\
%as suggested by \citet{Predehl2020}.

%Our discovery confirms the previously suggested common origin of the two objects \citep{Sofue2000,Kataoka2018}

>>>>

\begin{abstract}
A decade ago, the \textit{Fermi Gamma-Ray Space Telescope} reveals two large bubbles in the Galaxy,\
which extend nearly symmetrically $\sim50^{\circ}$ on either side of the Galactic disk.\

\end{abstract}

@@

  For these two reasons,\
  we have ignored the CR diffusion and the magnetic field throughout\
  the simulation.\
  Also, we do not simulate the spectral evolution of the CR\
  and assume the pressure ratio of CR to gas is much less than 1 so that\
  the contribution of CR pressure gradient to the momentum of the gas can be ignored.\
  (we will see that the pressure ratio is around 0.1--0.2 throughtout the bubbles formation)\
  Over and above, we neglect the cooling and heating processes of CRs,\
  such as energy losses due to synchrotron and inverse Compton emission,\
  and CR reacceleration in shocks/turbulences.

@@

In this work, we introduce a thin, dense disk composed of clumpy interstellar medium\
to divert the inclined jet at an angle $45^{\circ}$\
to the disk normal in the past energetic event of the central SMBH.

@@

\item The Galactic bubbles are nearly symmetric about the Galactic plane albeit the jet is at an angle $45^{\circ}$\
      with respect to the disc normal.\
      The broad agreement between simulated and observed multiwavelength features\
      provides supporting evidence for the inclined jet scenario, and also\
      releases the caveat given by earlier simulation-based studies:\
      the jets shall be vertical to the disc normal.
\item The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
      The ambient stratification facilitates the eROSITA bubbles elongation significantly.
      The development of the reverse shocks (the innermost bubbles) are always associated with the dense disc.
\item The edge of the eROSITA bubbles is a forward shock,\
      originally driven by oblique bipolar jets emanating from the GC 12.39 million years ago,\
      and significantly stretched by the stratified atmosphere afterwards.
\item Followed by the forward shock is a tangling contact discontinuity,\
      which we interpret as the edge of the \textit{Fermi} bubbles.\
      The nature of the \textit{Fermi} bubbles is essentially a turbulent and high-temperature ($\sim2$ keV)\
      plasma in pressure balance with the external medium. Associated with the Galactic magnetic field\
      will lead to the stochastic acceleration of CRe, and probably balanced with the IC and synchrotron cooling.\
      We will investigate the competition between CRe acceleration and radiative cooling in a future work.
\item According to the microwave and leptonic gamma-ray spectra, the best-fitting\
      CRe power-law index is found to be 2.4.
\item The same leptotonic CRe can simultaneously\
      account for the \textit{Fermi} bubbles and haze emission suggested that\
      they are physically related around the GC,\
      and that the magnetic fields within the bubbles are close to the exponentially distributed\
      Galactic magnetic field.
\end{itemize}
